---
title: "CBS Social Survey Report"
subtitle: "Version 08"
date: last-modified
author: "Saar Alon-Barkat, University of Haifa"
format:
  html:
    self-contained: true
    code-fold: true
    toc: true
    toc-location: left
execute:
  message: false
  warning: false
---

```{r}
library(tidyverse)
library(gt)
library(gtsummary)
library(janitor)
library(sjPlot)
library(ggcorrplot)
Sys.setlocale("LC_ALL","Herbrew")
```

<br>

This report summarizes first results from Israel CBS social surveys in years 2015-2021, focused on trust in government and trust in the judicary system.

**This is a preliminary report, reflecting work in progress. Please contact author before citing.**

Raw data obtained from the Israel CBS website: https://www.cbs.gov.il/he/subjects/Pages/%D7%94%D7%A1%D7%A7%D7%A8-%D7%94%D7%97%D7%91%D7%A8%D7%AA%D7%99.aspx

The data is analyzed and used in accordance with PUF license.

Information on the social survey available online at the Israel CBS website.

R code available at GitHub: https://github.com/saaralonbarkat/IL_CBS_social_survey

Statistical notes: 

- Analyses represent raw (unweighted) data, unless stated otherwise. Below, I also supplemented the main analyses with weights (using `nn` variable in the data - מקדמי ניפוח), and the differences were negligible. 

- Unless stated otherwise, percentages presented are raw percentages (i.e. missing data are included in the calculations). 


<br>


# **The data**

```{r}
lss_2015_raw<-read_csv("data/H20151311data.csv",na=c(NA,"999999","888888"))
lss_2016_raw<-read_csv("data/H20161342data.csv",na=c(NA,"999999","888888"))
lss_2017_raw<-read_csv("data/H20171353data.csv",na=c(NA,"999999","888888"))
lss_2018_raw<-read_csv("data/H20181362data.csv",na=c(NA,"999999","888888"))
lss_2019_raw<-read_csv("data/H20191424data.csv",na=c(NA,"999999","888888"))
lss_2020_raw<-read_csv("data/H20201453data.csv",na=c(NA,"999999","888888"))
lss_2021_raw<-read_csv("data/H20211461data.csv",na=c(NA,"999999","888888"))
```


```{r}

lss_total <- bind_rows(lss_2015_raw %>% janitor::clean_names(), 
                       lss_2016_raw %>% janitor::clean_names(), 
                       lss_2017_raw %>% janitor::clean_names(),
                       lss_2018_raw %>% janitor::clean_names(),
                       lss_2019_raw %>% janitor::clean_names(), 
                       lss_2020_raw %>% janitor::clean_names(), 
                       lss_2021_raw %>% janitor::clean_names()) %>%
  mutate(
    district = recode(
      machoz,
      `1` = "jerusalem",
      `2` = "north",
      `3` = "haifa",
      `4` = "center",
      `5` = "tel_aviv",
      `6` = "south",
      `7` = "yosh"
    ),
    subdistrict = nafa,
    residense_type = zurat_yishuv,
    religion = recode(
      dat,
      `1` = "1. jewish",
      `2` = "2. muslim",
      `3` = "3. christian",
      `4` = "4. druze",
      `5` = "5. other",
      `6` = "6. no_religion"
    ),
    year = recode(
      shana,
      `15` = 2015,
      `16` = 2016,
      `17` = 2017,
      `18` = 2018,
      `19` = 2019,
      `20` = 2020,
      `21` = 2021
    ) %>% replace_na(2016),
    trust_in_gov = recode(
      emun_memshala,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_gov_bi_excluding_na = recode(
      emun_memshala,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),    
    trust_in_gov_bi = recode(
      emun_memshala,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ) %>% replace_na(0),
    trust_in_judiciary = recode(
      emun_mishpat,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_judiciary_bi_excluding_na = recode(
      emun_mishpat,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_judiciary_bi = recode(
      emun_mishpat,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ) %>% replace_na(0),
    distrust_in_judiciary_bi = recode(
      emun_mishpat,
      `1` = 0,
      `2` = 0,
      `3` = 1,
      `4` = 1
    ) %>% replace_na(0),
    religiosity_level_jews = case_when(
      datiut_yehudi==1 ~ "1. Haredi",
      datiut_yehudi==2 ~ "2. Dati",
      datiut_yehudi==3 ~ "3. Masorty dati",
      datiut_yehudi==4 ~ "4. Masorty lo col cah dati",
      datiut_yehudi==5 ~ "5. Hilony",
      datiut_yehudi %in% NA & pop_group==1 ~ "Other (non Arab)"),
        religiosity_level_jews_lab = case_when(
      datiut_yehudi==1 ~ "1. חרדים",
      datiut_yehudi==2 ~ "2. דתיים",
      datiut_yehudi==3 ~ "3. מסורתיים דתיים",
      datiut_yehudi==4 ~ "4. מסורתיים לא כל כך דתיים",
      datiut_yehudi==5 ~ "5. חילונים",
      datiut_yehudi %in% NA & pop_group==1 ~ "אחר",
      pop_group==2 ~ "ערבים"),
    arab = ifelse(pop_group == 2, 1, 0),
    ultra_orthodox = ifelse(datiut_yehudi == 1, 1, 0),
    russian_ole = ifelse(yelid_brham == 1, 1, 0)) %>% 
  mutate(mizrahi_origin = ifelse(
      arab == 0 &
        (
          semel_eretz %in% c(3, 4) |
            semel_eretz_av_c %in% c(3, 4) | semel_eretz_em_c %in% c(3, 4)
        ),
      1,
      0
    ),
    gender = recode(minn, `1` = "male", `2` = "female"),
    age = recode(
      gil,
      `1` = "20-24",
      `2` = "25-29",
      `3` = "30-34",
      `4` = "34-39",
      `5` = "40-44",
      `6` = "45-49",
      `7` = "50-54",
      `8` = "55-59",
      `9` = "60-64",
      `10` = "65-74",
      `11` = "75_plus"
    ),
    household_income = recode(
      hachnasa_kolelet_neto,
      `1` = "1. 0-2500",
      `2` = "2. 2500-4000",
      `3` = "3. 4000-5000",
      `4` = "4. 5000-6500",
      `5` = "5. 6500-8000",
      `6` = "6. 8000-10000",
      `7` = "7. 10000-13000",
      `8` = "8. 13000-17000",
      `9` = "9. 17000-24000",
      `10` = "10. 24000+",
      `11` = "11. no_income"
    )) %>% 
  mutate(
    sector = case_when(
      arab == 1 ~ "arab",
      ultra_orthodox == 1 ~ "ultra_orthodox",
      TRUE ~ "general"
    ),
      arab_lab = recode(
      arab,
      `0` = "יהודים ואחרים",
      `1` = "ערבים"))


lss_total %>% count(arab,
                    religiosity_level_jews,
                    religiosity_level_jews_lab)
```

```{r}
lss_total%>%
  group_by(year)%>%
  summarize(n_participants=n())%>%
  gt()
```


```{r}
lss_total%>%
  select(year,
         gender,
         sector,
         religion,
         religiosity_level_jews,
         religiosity_level_jews_lab,
         age,
         district,
         household_income,
         russian_ole,
         trust_in_gov,
         trust_in_gov_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi)%>%  tbl_summary()
```

```{r}
lss_total%>%
  select(year,
         gender,
         sector,
         religion,
         religiosity_level_jews,
         age,
         district,
         subdistrict,
         household_income,
         russian_ole,
         trust_in_gov,
         trust_in_gov_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi)%>%
  tbl_summary(by=year)
```

```{r}
lss_total%>%
  select(year,
         gender,
         sector,
         religion,
         religiosity_level_jews,
         age,
         district,
         subdistrict,
         household_income,
         russian_ole,
         trust_in_gov,
         trust_in_gov_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi)%>%
  tbl_summary(by=sector)
```


```{r}
lss_total%>%
  select(year,
         gender,
         sector,
         religion,
         religiosity_level_jews,
         age,
         district,
         subdistrict,
         household_income,
         russian_ole,
         trust_in_gov,
         trust_in_gov_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi)%>%
  tbl_summary(by=religiosity_level_jews)

```

# **Attitudinal/trust variables**

**Trust in government:**

original item (EmunMemshala):
האם את/ה נותן/נותנת אמון בממשלה? 1- בכלל לא 2- לא כל כך 3- כן, במידה מסוימת 4- כן, במידה רבה

trust_in_gov_bi - 
high trust and trust to some degree = 1; not trust at all and not so much = 0; NA = 0


**Trust in the judiciary system:**

original item (emun_mishpat):
האם אתה נותן אמון במערכת המשפט?
1- בכלל לא
2- לא כל כך
3- כן, במידה מסוימת
4- כן, במידה רבה

trust_in_judiciary_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0; NA = 0


# **Findings**



## **Trust in government**

```{r}

t1<-lss_total%>%
  #drop_na(trust_in_gov)%>%
  group_by(trust_in_gov)%>%
  summarize(n=n())%>%
mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t1%>%
  #drop_na(trust_in_gov)%>%
  ggplot(aes(x=factor(trust_in_gov),y=freq*100))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  scale_x_discrete(breaks=c("1","2","3","4",NA),
        labels=c("בכלל לא", 
                 "לא כל כך", 
                 "במידה מסויימת",
                 "במידה רבה",
                 "לא ידוע"))+
  labs(title="?האם את/ה נותן/ת אמון בממשלה",
       subtitle = "2015-2021, משולב",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+  
    scale_y_continuous(
    labels = scales::percent_format(scale = 1)
  )+
  scale_color_viridis_d()+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )
```





```{r}
lss_total%>%  
  #drop_na(trust_in_gov)%>%
  ggplot(aes(x=year,y=(trust_in_gov_bi*100)))+
  stat_summary(geom="point",fun.data=mean_cl_boot)+
    stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="נותנים אמון בממשלה %",
       subtitle = "",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לסך האוכלוסייה נאמד בכ1.2%")+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))
```

```{r}
lss_total%>%
  ggplot(aes(x=year,y=trust_in_gov_bi*100,color=factor(arab)))+
  stat_summary(geom="point",fun.data=mean_cl_boot)+
  stat_summary(geom="line",fun.data=mean_cl_boot)+
  stat_summary(aes(group=1,shape="סהכ"),geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(aes(group=1,shape="סהכ"),geom="line",fun.data=mean_cl_boot,size=1)+
  labs(title="נותנים אמון בממשלה %",
       subtitle = "",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לסך האוכלוסייה נאמד בכ1.2%")+
  scale_color_viridis_d(labels=c('יהודים',
                                 'ערבים'))+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))
```




```{r}
lss_total%>%
  filter(datiut_yehudi<=5)%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi*100,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(geom="line",fun.data=mean_cl_boot,size=0.5)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="line",fun.data=mean_cl_boot,size=1)+
  labs(title="נותנים אמון בממשלה %",
       subtitle = "אוכלוסייה יהודית",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לאוכלוסייה היהודית סהכ נאמד בכ1.4%")+
  scale_color_viridis_d(labels=c('חרדים',
                                 'דתיים',
                                 'מסורתיים דתיים',
                                 'מסורתים לא דתיים',
                                 'חילונים'))+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))

```


## **Trust in the judiciary system:**

```{r}
t1<-lss_total%>%
  group_by(trust_in_judiciary)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))


t1%>%
  #drop_na(trust_in_judiciary)%>%
  ggplot(aes(x=factor(trust_in_judiciary),y=freq*100))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  scale_x_discrete(breaks=c("1","2","3","4",NA),
        labels=c("בכלל לא", 
                 "לא כל כך", 
                 "במידה מסויימת",
                 "במידה רבה",
                 "לא ידוע"))+
  labs(title="?האם את/ה נותן/ת אמון במערכת המשפט",
       subtitle = "2015-2021, משולב",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+  
    scale_y_continuous(
    labels = scales::percent_format(scale = 1)
  )+
  scale_color_viridis_d()+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )
```

```{r,fig.width=8}
t10<-lss_total%>%
  #drop_na(trust_in_judiciary)%>%
  group_by(year,trust_in_judiciary)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t10%>%
  #drop_na(trust_in_judiciary)%>%
  ggplot(aes(x=factor(trust_in_judiciary),y=n))+
  geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=2)+
  scale_x_discrete(breaks=c("1","2","3","4",NA),
        labels=c("בכלל לא", 
                 "לא כל כך", 
                 "במידה מסויימת",
                 "במידה רבה",
                 "לא ידוע"))+
  labs(title="?האם את/ה נותן/ת אמון במערכת המשפט",
       subtitle = "",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+ 
  facet_wrap(vars(year))+
  scale_color_viridis_d()+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )

```


```{r}

lss_total%>%
  ggplot(aes(x=year,y=(trust_in_judiciary_bi*100)))+
  stat_summary(geom="point",fun.data=mean_cl_boot)+
    stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="נותנים אמון במערכת המשפט %",
       subtitle = "",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לסך האוכלוסייה נאמד בכ1.2%")+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))
```


```{r}

lss_total%>%
  ggplot(aes(x=year,y=trust_in_judiciary_bi*100,color=factor(arab)))+
  stat_summary(geom="point",fun.data=mean_cl_boot)+
  stat_summary(geom="line",fun.data=mean_cl_boot)+
  stat_summary(aes(group=1,shape="סהכ"),geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(aes(group=1,shape="סהכ"),geom="line",fun.data=mean_cl_boot,size=1)+
  labs(title="נותנים אמון במערכת המשפט %",
       subtitle = "",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לסך האוכלוסייה נאמד בכ1.2%")+
   scale_color_viridis_d(labels=c('יהודים',
                                 'ערבים'))+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))
```

```{r}

t1 <- lss_total

t1$religiosity_level_jews <- factor(t1$religiosity_level_jews, 
                                    levels = c("5. Hilony",
                                               "4. Masorty lo col cah dati",
                                               "3. Masorty dati",
                                               "2. Dati",
                                               "1. Haredi"))

p2 <- t1%>%
  filter(datiut_yehudi<=5)%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi*100,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(geom="line",fun.data=mean_cl_boot,size=0.5)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="line",fun.data=mean_cl_boot,size=1)+
  labs(title="נותנים אמון במערכת המשפט %",
       subtitle = "אוכלוסייה יהודית",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לאוכלוסייה היהודית סהכ נאמד בכ1.4%")+
  scale_color_viridis_d(begin = 1,end=0,labels=c('חילונים',
                                 'מסורתים לא דתיים',
                                 'מסורתיים דתיים',
                                 'דתיים',
                                 'חרדים'))+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))

p2
```

```{r,fig.width=8}
p1 <- lss_total%>%
  filter(datiut_yehudi<=5)%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi*100,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(geom="line",fun.data=mean_cl_boot,size=0.5)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="line",fun.data=mean_cl_boot,size=1)+
  labs(title="נותנים אמון בממשלה %",
       x="",
       y="",
       color="",
       shape="",
       caption = "\n
       ")+
scale_color_viridis_d(labels=c('חרדים',
                                 'דתיים',
                                 'מסורתיים דתיים',
                                 'מסורתים לא דתיים',
                                 'חילונים'))+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))

t1 <- lss_total

t1$religiosity_level_jews <- factor(t1$religiosity_level_jews, 
                                    levels = c("5. Hilony",
                                               "4. Masorty lo col cah dati",
                                               "3. Masorty dati",
                                               "2. Dati",
                                               "1. Haredi"))

p2 <- lss_total%>%
  filter(datiut_yehudi<=5)%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi*100,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(geom="line",fun.data=mean_cl_boot,size=0.5)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="point",fun.data=mean_cl_boot,size=2)+
  stat_summary(aes(group=1,shape="סהכ יהודים"),geom="line",fun.data=mean_cl_boot,size=1)+
  labs(title="נותנים אמון במערכת המשפט %",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לאוכלוסייה היהודית סהכ נאמד בכ1.4%")+
  scale_color_viridis_d(labels=c('חילונים',
                                 'מסורתים לא דתיים',
                                 'מסורתיים דתיים',
                                 'דתיים',
                                 'חרדים'))+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7),
  axis.text = element_text(face="bold")
  )+
  coord_cartesian(ylim=c(15,80))


ggpubr:: ggarrange(p1,p2,
                   ncol=2,nrow=1,
                   common.legend = T,
                   legend = "right")
```



# For publication

## Unweighted

```{r}

lss_total_long <- lss_total %>% 
  pivot_longer(cols = c("trust_in_judiciary_bi","trust_in_gov_bi"),
               names_to = "institution",
               values_to = "trust_bi") %>%
  select(year,
         trust_bi,
         institution,
         sector,
         arab,
         arab_lab,
         religiosity_level_jews,
         religiosity_level_jews_lab) %>% 
  mutate(institution = institution %>% factor(levels = c("trust_in_judiciary_bi","trust_in_gov_bi"))) %>% 
  mutate(institution = recode(
      institution,
      `trust_in_judiciary_bi` = "אמון במערכת המשפט",
      `trust_in_gov_bi` = "אמון בממשלה"))
```



**Trust in government v. Knesset**

```{r}



lss_total_long %>%
  ggplot(aes(x=year,y=(trust_bi*100),color=institution))+
    stat_summary(aes(group=institution),geom="errorbar",fun.data=mean_cl_boot,color="gray80",width=0)+
    stat_summary(geom="point",fun.data=mean_cl_boot)+
    stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  labs(title="נותנים אמון %",
       subtitle = "במידה מסויימת או במידה רבה",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לסך האוכלוסייה נאמד בכ1.2%")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7)
  )+
  coord_cartesian(ylim=c(15,80))
```


```{r}
lss_total %>% 
  group_by(year) %>% 
  summarise(percent_trust_in_judiciary = trust_in_judiciary_bi %>% mean(na.rm=T),
            percent_trust_in_judiciary_exc_na = trust_in_judiciary_bi_excluding_na %>% mean(na.rm=T),
            percent_trust_in_government = trust_in_gov_bi %>% mean(na.rm=T),
            percent_trust_in_governmen_exc_na = trust_in_gov_bi_excluding_na %>% mean(na.rm=T)) %>% 
  mutate(percent_trust_in_judiciary=str_c(round(100*percent_trust_in_judiciary,1),"%"),
         percent_trust_in_government=str_c(round(100*percent_trust_in_government,1),"%"),
        percent_trust_in_judiciary_exc_na=str_c(round(100*percent_trust_in_judiciary_exc_na,1),"%"),
         percent_trust_in_governmen_exc_na=str_c(round(100*percent_trust_in_governmen_exc_na,1),"%")) %>% 
  gt()
  

```



**Jews v. Arabs**
```{r}

lss_total_long %>%
  ggplot(aes(x=year,y=(trust_bi*100),color=institution))+
      stat_summary(aes(group=institution),geom="errorbar",fun.data=mean_cl_boot,color="gray80",width=0)+
  stat_summary(geom="point",fun.data=mean_cl_boot)+
    stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  labs(title="נותנים אמון %",
       subtitle = "במידה מסויימת או במידה רבה",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  facet_grid(cols = vars(arab_lab))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7)
  )+
  coord_cartesian(ylim=c(15,80))
```


**Jews religiosity groups**
```{r,fig.width=6}

lss_total_long %>%
  ggplot(aes(x=year,y=(trust_bi*100),color=institution))+
        stat_summary(aes(group=institution),geom="errorbar",fun.data=mean_cl_boot,color="gray80",width=0)+
  stat_summary(geom="point",fun.data=mean_cl_boot)+
    stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  labs(title="נותנים אמון %",
       subtitle = "במידה מסויימת או במידה רבה",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  facet_wrap(vars(religiosity_level_jews_lab))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7)
  )+
  coord_cartesian(ylim=c(15,80))
```


## Weighted


weighted (with `srvyr`)
```{r}
library(srvyr)

lss_total_srvyr <- lss_total %>% as_survey_design(weights = nn)

```

```{r}

lss_total_long_srvyr <- lss_total %>% 
  pivot_longer(cols = c("trust_in_judiciary_bi","trust_in_gov_bi"),
               names_to = "institution",
               values_to = "trust_bi") %>%
  as_survey_design(weights = nn) %>%
  select(year,
         trust_bi,
         institution,
         sector,
         arab,
         arab_lab,
         religiosity_level_jews,
         religiosity_level_jews_lab) %>% 
  mutate(institution = institution %>% factor(levels = c("trust_in_judiciary_bi","trust_in_gov_bi"))) %>% 
  mutate(institution = recode(
      institution,
      `trust_in_judiciary_bi` = "אמון במערכת המשפט",
      `trust_in_gov_bi` = "אמון בממשלה"))
```


```{r}
t1 <- lss_total_long_srvyr %>%
  #drop_na(trust_in_gov_bi) %>%
    #filter(datiut_yehudi<=5)%>%
  group_by(year,institution)%>%
  summarize(mean_trust_weighted = survey_mean(trust_bi, vartype = "ci"))

t1 %>%
  ggplot(aes(x=year,y=(mean_trust_weighted*100),ymax = mean_trust_weighted_upp*100, ymin = mean_trust_weighted_low*100,color=institution))+
  geom_errorbar(color="gray80",width=0)+
  geom_point()+
  geom_line()+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  labs(title="נותנים אמון במערכת המשפט ובממשלה מכלל האוכלוסייה%",
       subtitle = "(במידה מסויימת או במידה רבה)",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21\n
       +-טווח הטעות התקנית לסך האוכלוסייה נאמד בכ1.2%")+
    scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7)
  )+
  coord_cartesian(ylim=c(15,80))
```

```{r}
t1 <- lss_total_long_srvyr %>%
  #drop_na(trust_in_gov_bi) %>%
    #filter(datiut_yehudi<=5)%>%
  group_by(year,institution,arab_lab)%>%
  summarize(mean_trust_weighted = survey_mean(trust_bi, vartype = "ci"))

t1 %>%
  ggplot(aes(x=year,y=(mean_trust_weighted*100),ymax = mean_trust_weighted_upp*100, ymin = mean_trust_weighted_low*100,color=institution))+
  geom_errorbar(color="gray80",width=0)+
  geom_point()+
  geom_line()+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  labs(title="נותנים אמון %",
       subtitle = "(במידה מסויימת או במידה רבה)",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+
    facet_grid(cols = vars(arab_lab))+
  scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7)
  )+
  coord_cartesian(ylim=c(15,80))
```




```{r,fig.width=6}
t1 <- lss_total_long_srvyr %>%
  #drop_na(trust_in_gov_bi) %>%
    #filter(datiut_yehudi<=5)%>%
  group_by(year,institution,religiosity_level_jews_lab)%>%
  summarize(mean_trust_weighted = survey_mean(trust_bi, vartype = "ci"))

t1 %>%
  filter(religiosity_level_jews_lab!="אחר") %>% 
  ggplot(aes(x=year,y=(mean_trust_weighted*100),ymax = mean_trust_weighted_upp*100, ymin = mean_trust_weighted_low*100,color=institution))+
  geom_errorbar(color="gray80",width=0)+
  geom_point()+
  geom_line()+
  geom_hline(yintercept = 50,linetype="dashed",color="gray80")+
  labs(title="נותנים אמון במערכת המשפט ובממשלה - לפי קבוצות %",
       subtitle = "(במידה מסויימת או במידה רבה)",
       x="",
       y="",
       color="",
       shape="",
       caption = "מקור: למס, הסקר החברתי, 2015-21")+
facet_wrap(vars(religiosity_level_jews_lab))+
  scale_y_continuous(
    labels = scales::percent_format(scale = 1),
    breaks = c(25, 50,75)
  )+
    scale_x_continuous(
    breaks = 2015:2021
  )+
  theme_classic()+
  theme(plot.title = element_text(hjust = 1,face="bold"),
  plot.subtitle = element_text(hjust = 1),
  plot.caption = element_text(hjust = 1,color = "gray50",size=7)
  )+
  coord_cartesian(ylim=c(15,80))
```


```{r}

t1 <- lss_total_srvyr %>%
    #drop_na(trust_in_gov)%>%
  group_by(trust_in_gov)%>%
  summarize(n=n(),
            proportion_weighted = survey_mean(),
            total_weighted = survey_total())%>%
mutate(freq_unweighted=(n/sum(n)))%>%
  mutate(proportion_weighted.lab=str_c(round(100*proportion_weighted,1),"%"))

t1

t1%>%
  #drop_na(trust_in_gov)%>%
  ggplot(aes(x=factor(trust_in_gov),y=proportion_weighted))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=proportion_weighted.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in Government",subtitle = "Weighted proportions",x="",y="")+
  scale_color_viridis_d()+
  theme_classic()
```


```{r}
t1 <- lss_total_srvyr %>%
  #drop_na(trust_in_gov_bi) %>%
    #filter(datiut_yehudi<=5)%>%
  group_by(year)%>%
  summarize(percent_trust_in_government_weighted = survey_mean(trust_in_gov_bi),
            percent_trust_in_government_unweighted = mean(trust_in_gov_bi),
            percent_trust_in_judiciary_weighted = survey_mean(trust_in_judiciary_bi),
            percent_trust_in_judiciary_unweighted = mean(trust_in_judiciary_bi)) %>% 
  mutate(percent_trust_in_government_weighted=str_c(round(100*percent_trust_in_government_weighted,1),"%"),
         percent_trust_in_government_unweighted=str_c(round(100*percent_trust_in_government_unweighted,1),"%"),
        percent_trust_in_judiciary_weighted=str_c(round(100*percent_trust_in_judiciary_weighted,1),"%"),
         percent_trust_in_judiciary_unweighted=str_c(round(100*percent_trust_in_judiciary_unweighted,1),"%")) %>% 
  gt()

t1


```

```{r}
t1 <- lss_total_srvyr %>%
  #drop_na(trust_in_gov_bi) %>%
    #filter(datiut_yehudi<=5)%>%
  group_by(year,religiosity_level_jews_lab)%>%
  summarize(percent_trust_in_government_weighted = survey_mean(trust_in_gov_bi),
            percent_trust_in_government_unweighted = mean(trust_in_gov_bi),
            percent_trust_in_judiciary_weighted = survey_mean(trust_in_judiciary_bi),
            percent_trust_in_judiciary_unweighted = mean(trust_in_judiciary_bi)) %>% 
  mutate(percent_trust_in_government_weighted=str_c(round(100*percent_trust_in_government_weighted,1),"%"),
         percent_trust_in_government_unweighted=str_c(round(100*percent_trust_in_government_unweighted,1),"%"),
        percent_trust_in_judiciary_weighted=str_c(round(100*percent_trust_in_judiciary_weighted,1),"%"),
         percent_trust_in_judiciary_unweighted=str_c(round(100*percent_trust_in_judiciary_unweighted,1),"%")) %>% 
  gt()

t1
```


