---
title: "CBS Social Survey Report"
subtitle: "Version 08"
date: last-modified
author: "Lior Shvarts"
format:
  html:
    self-contained: true
    code-fold: true
    toc: true
    toc-location: left
execute:
  message: false
  warning: false
---

```{r}
library(tidyverse)
library(gt)
library(gtsummary)
library(janitor)
library(sjPlot)
library(ggcorrplot)
Sys.setlocale("LC_ALL","Herbrew")
```

# **The data**

```{r}
lss_2019_raw<-read_csv("data/H20191424data.csv",na=c(NA,"999999","888888"))
lss_2020_raw<-read_csv("data/H20201453data.csv",na=c(NA,"999999","888888"))
lss_2021_raw<-read_csv("data/H20211461data.csv",na=c(NA,"999999","888888"))

lss_total <- bind_rows(lss_2019_raw, lss_2020_raw, lss_2021_raw) %>%
  janitor::clean_names() %>%
  mutate(
    district = recode(
      machoz,
      `1` = "jerusalem",
      `2` = "north",
      `3` = "haifa",
      `4` = "center",
      `5` = "tel_aviv",
      `6` = "south",
      `7` = "yosh"
    ),
    subdistrict = nafa,
    residense_type = zurat_yishuv,
    religion = recode(
      dat,
      `1` = "1. jewish",
      `2` = "2. muslim",
      `3` = "3. christian",
      `4` = "4. druze",
      `5` = "5. other",
      `6` = "6. no_religion"
    ),
    year = recode(
      shana,
      `19` = 2019,
      `20` = 2020,
      `21` = 2021
    ),
    performance_health = recode(
      tifkud_briut,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_gov = recode(
      emun_memshala,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_healthcare = recode(
      emun_briut,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_healthcare_bi = recode(
      emun_briut,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    performance_health_bi = recode(
      tifkud_briut,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_gov_bi = recode(
      emun_memshala,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    performance_education = recode(
      tifkud_hinuch,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    performance_education_bi = recode(
      tifkud_hinuch,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_police = recode(
      emun_mishtara,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_police_bi = recode(
      emun_mishtara,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    performance_police = recode(
      tifkud_mishtara,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    performance_police_bi = recode(
      tifkud_mishtara,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    performance_municipality = recode(
      tifkud_iriya,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    performance_municipality_bi = recode(
      tifkud_iriya,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_knesset = recode(
      emun_kneset,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_knesset_bi = recode(
      emun_kneset,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    performance_knesset = recode(
      tifkud_kneset,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    performance_knesset_bi = recode(
      tifkud_kneset,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_judiciary = recode(
      emun_mishpat,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_judiciary_bi = recode(
      emun_mishpat,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_army = recode(
      emun_tzahal,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_army_bi = recode(
      emun_tzahal,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    trust_in_comptroller = recode(
      emun_mevaker,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    trust_in_comptroller_bi = recode(
      emun_mevaker,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    satisfied_area = recode(
      merutze_ezor,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    satisfied_area_bi = recode(
      merutze_ezor,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    satisfied_transport = recode(
      merutze_tachbura,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ) %>% na_if(5),
    satisfied_transport_bi = recode(
      merutze_tachbura,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ) %>% na_if(5),
    satisfied_parks = recode(
      merutze_ezor_parkim,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    satisfied_parks_bi = recode(
      merutze_ezor_parkim,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    satisfied_clean = recode(
      merutze_ezor_nikayon,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    satisfied_clean_bi = recode(
      merutze_ezor_nikayon,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    satisfied_trash = recode(
      merutze_ezor_ashpa,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    satisfied_trash_bi = recode(
      merutze_ezor_ashpa,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    satisfied_roads = recode(
      merutze_kvishim,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
    ),
    satisfied_roads_bi = recode(
      merutze_kvishim,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ),
    religiosity_level_jews = case_when(
      datiut_yehudi==1 ~ "1. Haredi",
      datiut_yehudi==2 ~ "2. Dati",
      datiut_yehudi==3 ~ "3. Masorty dati",
      datiut_yehudi==4 ~ "4. Masorty lo col cah dati",
      datiut_yehudi==5 ~ "5. Hilony",
      datiut_yehudi %in% NA & pop_group==1 ~ "Other (non Arab)"),
    feel_safe = recode(
      margish_batuach,
      `1` = 4,
      `2` = 3,
      `3` = 2,
      `4` = 1
      ) %>% na_if(5),
    feel_safe_bi = recode(
      margish_batuach,
      `1` = 1,
      `2` = 1,
      `3` = 0,
      `4` = 0
    ) %>% na_if(5),
    reside_own_apartment = recode(
      dira_baalut,
      `1` = 1,
      `2` = 0
      ),
    own_apartment = recode(
      dira_baalut_c,
      `1` = 1,
      `2` = 0
      ),
    arab = ifelse(pop_group == 2, 1, 0),
    ultra_orthodox = ifelse(datiut_yehudi == 1, 1, 0),
    russian_ole = ifelse(yelid_brham == 1, 1, 0)) %>% 
  mutate(mizrahi_origin = ifelse(
      arab == 0 &
        (
          semel_eretz %in% c(3, 4) |
            semel_eretz_av_c %in% c(3, 4) | semel_eretz_em_c %in% c(3, 4)
        ),
      1,
      0
    ),
    gender = recode(minn, `1` = "male", `2` = "female"),
    age = recode(
      gil,
      `1` = "20-24",
      `2` = "25-29",
      `3` = "30-34",
      `4` = "34-39",
      `5` = "40-44",
      `6` = "45-49",
      `7` = "50-54",
      `8` = "55-59",
      `9` = "60-64",
      `10` = "65-74",
      `11` = "75_plus"
    ),
    household_income = recode(
      hachnasa_kolelet_neto,
      `1` = "1. 0-2500",
      `2` = "2. 2500-4000",
      `3` = "3. 4000-5000",
      `4` = "4. 5000-6500",
      `5` = "5. 6500-8000",
      `6` = "6. 8000-10000",
      `7` = "7. 10000-13000",
      `8` = "8. 13000-17000",
      `9` = "9. 17000-24000",
      `10` = "10. 24000+",
      `11` = "11. no_income"
    )) %>% 
  mutate(
    sector = case_when(
      arab == 1 ~ "arab",
      ultra_orthodox == 1 ~ "ultra_orthodox",
      TRUE ~ "general"
    )) %>% 
  mutate(
    sector_multiple = case_when(
      arab == 1 & religion == "3. christian" ~ "Arab Christians",
      religion == "4. druze" ~ "Arab Druzes",
      arab == 1 &
        religion == "2. muslim" & residense_type != 1 ~ "Arab Muslims",
      arab == 1 &
        residense_type == 1 ~ "Arab Jerusalem",
      ultra_orthodox == 1 ~ "Jewish Ultra Orthodox",
      russian_ole == 1 ~ "Jewish USSR born",
      mizrahi_origin == 1 &
        ultra_orthodox == 0 ~ "Jewish Mizrahi Origin",
      arab == 0 &
        mizrahi_origin == 0 & ultra_orthodox == 0 ~ "Jewish Ashkenazi",
      TRUE ~ "Other"
    )
  )


        
```

```{r}
lss_total%>%
  group_by(year)%>%
  summarize(n_participants=n())%>%
  gt()
```

```{r}
lss_total%>%
  select(year,
         gender,
         sector,
         sector_multiple,
         religion,
         religiosity_level_jews,
         age,
         district,
         subdistrict,
         residense_type,
         household_income,
         russian_ole,
         mizrahi_origin,
         reside_own_apartment,
         own_apartment,
         performance_health,
         performance_health_bi,
         trust_in_gov,
         trust_in_gov_bi,
         performance_health,
         performance_health_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  glimpse()
```

```{r}
lss_total%>%
  select(year,gender,sector,sector_multiple,religion,religiosity_level_jews,age,district,household_income,own_apartment,own_apartment)%>%
  tbl_summary()
```

```{r}
lss_total%>%
  select(year,gender,sector,sector_multiple,religion,religiosity_level_jews,age,district,household_income,own_apartment,own_apartment)%>%
  tbl_summary(by=year)
```

```{r}
lss_total%>%
  select(year,gender,sector,sector_multiple,religion,religiosity_level_jews,age,district,household_income,own_apartment,own_apartment)%>%
  tbl_summary(by=sector)
```

```{r}
lss_total%>%
  select(year,gender,sector_multiple,religion,religiosity_level_jews,age,district,household_income,own_apartment,own_apartment)%>%
  tbl_summary(by=sector_multiple)
```

```{r}
lss_total%>%
   select(year,gender,sector_multiple,religion,religiosity_level_jews,age,district,household_income,own_apartment,own_apartment)%>%
  tbl_summary(by=own_apartment)
```

```{r}
lss_total%>%
     select(year,gender,sector_multiple,religion,religiosity_level_jews,age,district,household_income,own_apartment,own_apartment)%>%
  tbl_summary(by=own_apartment)
```

# **Sectors**

Categorization of sectors:

1.  General
2.  Ultra Orthodox
3.  Arab

Categorization of sub-sectors:

1.  Arab Christians
2.  Arab Druze
3.  Arab Jerusalem (belongs to Arab population and residing in Jerusalem)
4.  Arab Muslim
5.  Jewish Ultra-Orthodox (based on self reporting of level of religiousity among Jews)
6.  Jewish USSR born
7.  Jewish Mizrahi origin (either born in Asia/Africa or mother/father born in Asia/Africa)
8.  Jewish Ashkenazi (Jewish, residual category)
9.  Other (non Jewish residual category)

Categorization of level of religiosity (for Jews):

1. Ultra Orthodox
2. Religious
3. Traditionalists (religious)
4. Traditionalists (not so religious)
5. Secular (non-religious)

# **Attitudinal/trust variables**

## **1. GOVERNMENT**

**Trust in government:**

original item (EmunMemshala): האם את/ה נותן/נותנת אמון בממשלה? 1- בכלל לא 2- לא כל כך 3- כן, במידה מסוימת 4- כן, במידה רבה

trust_in_gov_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0

## **2. HEALTHCARE SYSTEM**

**Trust in healthcare system:**

original item (EmunBriut): האם את/ה נותן/נותנת אמון במערכת הבריאות? 1- בכלל לא 2- לא כל כך 3- כן, במידה מסוימת 4- כן, במידה רבה

trust_healthcare_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0

**Performance evaluation of healthcare system:**

original item (TifkudBriut): מה דעתך על תפקוד מערכת הבריאות? 1- בכלל לא טוב 2- לא כל כך טוב 3- טוב 4-טוב מאוד

performance_health_bi - good and very good = 1; not so good and not good at all = 0

## **3. EDUCATION SYSTEM**

**Performance evaluation of education system:**

original item (tifkud_hinuch):
מה דעתך על תפקוד מערכת החינוך? 
1- בכלל לא טוב
2- לא כל כך טוב
3- טוב
4- טוב מאוד

performance_education_bi - good and very good = 1; not so good and not good at all = 0

## **4. POLICE**

**Performance evaluation of the police:**

original item (tifkud_mishtara):
מה דעתך על תפקוד משטרת ישראל?
1- בכלל לא טוב
2- לא כל כך טוב
3- טוב
4- טוב מאוד

performance_police_bi - good and very good = 1; not so good and not good at all = 0

**Trust in the police:**

original item (emun_mishtara):
האם אתה נותן אמון במשטרת ישראל?
1- בכלל לא
2- לא כל כך
3- כן, במידה מסוימת
4- כן, במידה רבה

trust_in_police_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0

## **5. MUNICIPALITY**

**Performance evaluation of the municipality:**

original item (tifkud_iriya):
מה דעתך על תפקוד העירייה/ הרשות המקומית?
1- בכלל לא טוב
2- לא כל כך טוב
3- טוב
4- טוב מאוד

performance_municipality_bi - good and very good = 1; not so good and not good at all = 0

## **6. KNESSET**

**Trust in the Knesset:**

original item (emun_kneset):
האם אתה נותן אמון בכנסת?
1- בכלל לא
2- לא כל כך
3- כן, במידה מסוימת
4- כן, במידה רבה

trust_in_knesset_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0

**Performance evaluation of the Knesset:**

original item (tifkud_kneset):
מה דעתך על תפקוד הכנסת?
1- בכלל לא טוב
2- לא כל כך טוב
3- טוב
4- טוב מאוד

performance_knesset_bi - good and very good = 1; not so good and not good at all = 0

## **7. JUDICIARY**

**Trust in the judiciary system:**

original item (emun_mishpat):
האם אתה נותן אמון במערכת המשפט?
1- בכלל לא
2- לא כל כך
3- כן, במידה מסוימת
4- כן, במידה רבה

trust_in_judiciary_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0

## **8. ARMY**

**Trust in the army:**

original item (emun_tzahal):
האם אתה נותן באמון בצה"ל?
1- בכלל לא
2- לא כל כך
3- כן, במידה מסוימת
4- כן, במידה רבה

trust_in_army_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0

## **9. STATE COMPTROLLER**

**Trust in the state comptroller:**

original item (emun_mevaker):
האם אתה נותן אמון במבקר המדינה?
1- בכלל לא
2- לא כל כך
3- כן, במידה מסוימת
4- כן, במידה רבה

trust_in_comptroller_bi - high trust and trust to some degree = 1; not trust at all and not so much = 0


## **Local Services:**

### **13. Satisfaction with the place of residence:**

original item (merutze_ezor):
באופן  כללי, האם אתה מרוצה מהאזור שבו אתה גר?
1- בכלל לא מרוצה
2- לא כל כך מרוצה
3- מרוצה
4- מרוצה מאוד

satisfied_area_bi - satisfied and very satisfied = 1; not satisfied and not satisfied at all = 0

### **14. Satisfaction with the public transportation in the place of residence:**

original item (merutze_tachbura):
האם אתה מרוצה מהתחבורה הציבורית באזור מגוריך?
1- בכלל לא מרוצה
2- לא כל כך מרוצה
3- מרוצה
4- מרוצה מאוד
5- לא משתמש בתחבורה ציבורית

### **15. Satisfaction with green spaces, public gardens and parks in place of residence:**

original item (merutze_ezor_parkim):
האם אתה מרוצה מכמות השטחים הירוקים, הגנים הציבוריים או הפארקים באזור בו אתה גר?
1- בכלל לא מרוצה
2- לא כל כך מרוצה
3- מרוצה
4- מרוצה מאוד

### **16. Satisfaction with the cleanliness of the place of residence:**

original item (merutze_ezor_nikayon):
האם אתה מרוצה מהניקיון באזור בו אתה גר?
1- בכלל לא מרוצה
2- לא כל כך מרוצה
3- מרוצה
4- מרוצה מאוד

### **17. Satisfaction with garbage collection in place of residence:**

original item (merutze_ezor_ashpa):
האם אתה מרוצה משירותי איסוף האשפה באזור מגוריך?
1- בכלל לא מרוצה
2- לא כל כך מרוצה
3- מרוצה
4- מרוצה מאוד

### **18. Satisfaction with the condition of the roads and sidewalks in place of residence:**

original item (merutze_ezor_kvishim):
האם אתה מרוצה ממצב הכבישים והמדרכות באזור שבו אתה גר? כגון: רוחב הכבישים והמדרכות, תאורה מספקת, שילוט וכדומה
1- בכלל לא מרוצה
2- לא כל כך מרוצה
3- מרוצה
4- מרוצה מאוד

### **19. Feeling safe while walking alone in the hours of darkness in the place of residence:**

original item (margish_batuach):
האם אתה מרגיש בטוח ללכת לבדך בשעות החשיכה באזור בו אתה גר?
1- בכלל לא בטוח
2- לא כל כך בטוח
3- בטוח
4- בטוח מאוד
5- לא יוצא מהבית


# **Findings**



## **1. Trust in government:**

```{r}
t1<-lss_total%>%
  group_by(trust_in_gov)%>%
  summarize(n=n())%>%
mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t1%>%
  drop_na(trust_in_gov)%>%
  ggplot(aes(x=factor(trust_in_gov),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in Government",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(trust_in_gov_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in government by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in government by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in government by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")

lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
      facet_grid(cols=vars(mizrahi_origin))+
  labs(title="% having trust in government by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in government by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_in_gov,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in government by age group",subtitle="(mean+95CI)",x="age group",y="",caption="2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_in_gov,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in government by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in government by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_gov_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in government by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **2. Trust in health system:**

```{r}
t2<-lss_total%>%
  filter(year==2019&2020)%>%
  group_by(trust_healthcare)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t2%>%
  drop_na(trust_healthcare)%>%
  ggplot(aes(x=factor(trust_healthcare),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in health system",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(trust_healthcare_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in government by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_healthcare_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in health system by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_healthcare_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in health system by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_healthcare_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in health system by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_healthcare_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% trust in health system by age group",subtitle="(mean+95CI)",x="age group",y="",caption="2019-2020")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_healthcare_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in health system by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2020")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_healthcare_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in health system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")

```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_healthcare_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in health system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_healthcare_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in health system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **3. Performance evaluation of healthcare system:**

```{r}
t3<-lss_total%>%
  group_by(performance_health)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t3%>%
  drop_na(performance_health)%>%
  ggplot(aes(x=factor(performance_health),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Evaluation of health services",x="",y="")

```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(performance_health_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Positive evaluation of health services by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_health_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of health services by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_health_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% positive evaluation of health system by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_health_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of health services by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=performance_health_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of health services by age group",subtitle="(mean+95CI)",x="",y="",caption="evaluation of health services, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=performance_health_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of health services by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_health_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% positive evaluation of health services by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_health_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% positive evaluation of health services by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **4. Performance evaluation of education system:**

```{r}
t4<-lss_total%>%
  group_by(performance_education)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t4%>%
  drop_na(performance_education)%>%
  ggplot(aes(x=factor(performance_education),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Evaluation of education system",x="",y="")

```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_education_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of education system by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_education_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% positive evaluation of health system by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_education_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of education system by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=performance_education_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of health services by age group",subtitle="(mean+95CI)",x="",y="",caption="evaluation of education system, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=performance_education_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of education system by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_education_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% positive evaluation of education system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")

```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_education_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% positive evaluation of education system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_education_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% positive evaluation of education system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **5. Trust in the police:**

```{r}
t5<-lss_total%>%
  filter(year==2021)%>%
  group_by(trust_in_police)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t5%>%
  drop_na(trust_in_police)%>%
  ggplot(aes(x=factor(trust_in_police),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in the police",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_in_police_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the police by age group",subtitle="(mean+95CI)",x="",y="",caption="trust in the police, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector,y=trust_in_police_bi,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the police by sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the police, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector_multiple,y=trust_in_police_bi,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the police by sub-sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the police, normalized (0 to 1), 2021")+
  coord_flip()
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_in_police_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the police by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2021")+
  coord_flip()
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  ggplot(aes(x=factor(own_apartment),y=trust_in_police_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in the police by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_police_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in the police by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

## **6. Performance evaluation of the police:**

```{r}
t6<-lss_total%>%
  group_by(performance_police)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t6%>%
  drop_na(performance_police)%>%
  ggplot(aes(x=factor(performance_police),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Evaluation of the police",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(performance_police_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Positive evaluation of the police by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_police_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the police by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_police_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the police by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_police_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the police by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=performance_police_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the police by age group",subtitle="(mean+95CI)",x="",y="",caption="evaluation of the police, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=performance_police_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the police by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_police_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% positive evaluation of the police by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_police_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% positive evaluation of the police by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **7. Performance evaluation of the municipality:**

```{r}
t7<-lss_total%>%
  group_by(performance_municipality)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t7%>%
  drop_na(performance_municipality)%>%
  ggplot(aes(x=factor(performance_municipality),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Evaluation of the municipality",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(performance_municipality_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Positive evaluation of the municipality by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_municipality_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the municipality by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_municipality_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the municipality by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_municipality_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the municipality by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=performance_municipality_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the municipality by age group",subtitle="(mean+95CI)",x="",y="",caption="evaluation of the municipality, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=performance_municipality_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the municipality by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_municipality_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% positive evaluation of the municipality by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_municipality_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% positive evaluation of the municipality by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **8. Trust in the Knesset:**

```{r}
t8<-lss_total%>%
  filter(year==2021)%>%
  group_by(trust_in_knesset)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t8%>%
  drop_na(trust_in_knesset)%>%
  ggplot(aes(x=factor(trust_in_knesset),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in the Knesset",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_in_knesset_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the Knesset by age group",subtitle="(mean+95CI)",x="",y="",caption="trust in the Knesset, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector,y=trust_in_knesset_bi,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the Knesset by sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the Knesset, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector_multiple,y=trust_in_knesset_bi,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the Knesset by sub-sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the Knesset, normalized (0 to 1), 2021")+
  coord_flip()
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_in_knesset_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the Knesset by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2021")+
  coord_flip()
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  ggplot(aes(x=factor(own_apartment),y=trust_in_knesset_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in the Knesset by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_knesset_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in the Knesset by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

## **9. Performance evaluation of the Knesset:**

```{r}
t9<-lss_total%>%
  group_by(performance_knesset)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t9%>%
  drop_na(performance_knesset)%>%
  ggplot(aes(x=factor(performance_knesset),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Evaluation of the Knesset",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(performance_knesset_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Positive evaluation of the Knesset by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_knesset_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the Knesset by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_knesset_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the Knesset by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_knesset_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the Knesset by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=performance_knesset_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the Knesset by age group",subtitle="(mean+95CI)",x="",y="",caption="trust in the Knesset, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=performance_knesset_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% positive evaluation of the Knesset by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=performance_knesset_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% positive evaluation of the Knesset by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=performance_knesset_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% positive evaluation of the Knesset by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **10. Trust in the judiciary system:**

```{r}
t10<-lss_total%>%
  group_by(trust_in_judiciary)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t10%>%
  drop_na(trust_in_judiciary)%>%
  ggplot(aes(x=factor(trust_in_judiciary),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in the judiciary system",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(trust_in_judiciary_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the judiciary system by year",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in the judiciary system by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Positive evaluation of the judiciary system by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% having trust in the judiciary system by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_in_judiciary_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the judiciary system by age group",subtitle="(mean+95CI)",x="",y="",caption="trust in the judiciary system, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_in_judiciary_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the judiciary system by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in the judiciary system by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_judiciary_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in the judiciary by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

## **11. Trust in the army:**

```{r}
t11<-lss_total%>%
  filter(year==2021)%>%
  group_by(trust_in_army)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t11%>%
  drop_na(trust_in_army)%>%
  ggplot(aes(x=factor(trust_in_army),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in the army",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_in_army_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the army by age group",subtitle="(mean+95CI)",x="",y="",caption="trust in the army, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector,y=trust_in_army_bi,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the army by sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the army, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector_multiple,y=trust_in_army_bi,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the army by sub-sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the army, normalized (0 to 1), 2021")+
  coord_flip()
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_in_army_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the army by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2021")+
  coord_flip()
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  ggplot(aes(x=factor(own_apartment),y=trust_in_army_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in the army by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_army_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in the army by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

## **12. Trust in the state Comptroller:**

```{r}
t12<-lss_total%>%
  filter(year==2021)%>%
  group_by(trust_in_comptroller)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t12%>%
  drop_na(trust_in_comptroller)%>%
  ggplot(aes(x=factor(trust_in_comptroller),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Trust in the state comptroller",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=trust_in_comptroller_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the state comptroller by age group",subtitle="(mean+95CI)",x="",y="",caption="trust in the state comptroller, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector,y=trust_in_comptroller_bi,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the state comptroller by sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the state comptroller, normalized (0 to 1), 2021")
```

```{r}
lss_total%>%
  ggplot(aes(x=sector_multiple,y=trust_in_comptroller_bi,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the state comptroller by sub-sector",subtitle="(mean+95CI)",x="",y="",caption="trust in the state comptroller, normalized (0 to 1), 2021")+
  coord_flip()
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=trust_in_comptroller_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% having trust in the state comptroller by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2021")+
  coord_flip()
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  ggplot(aes(x=factor(own_apartment),y=trust_in_comptroller_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% having trust in the state comptroller by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

```{r}
lss_total%>%
  filter(year==2021)%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=trust_in_comptroller_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% having trust in the state comptroller by home ownership",subtitle="(mean+95CI)",x="",y="",caption="2021")
```

## **Findings - local services:**

### **13. Satisfaction with the place of residence:**

```{r}
t13<-lss_total%>%
  group_by(satisfied_area)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t13%>%
  drop_na(satisfied_area)%>%
  ggplot(aes(x=factor(satisfied_area),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="satisfaction with the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(satisfied_area_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_area_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_area_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the place of residence by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_area_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=satisfied_area_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="satisfaction with the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=satisfied_area_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_area_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(sector))+
  labs(title="% satisfied with the place of residence by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_area_bi,color=factor(own_apartment),group=own_apartment))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
        facet_grid(cols=vars(religiosity_level_jews))+
  labs(title="% satisfied with the place of residence by year and home ownership",subtitle="(mean+95CI)",x="",y="",caption="")
```

### **14. Satisfaction with the public transportation in the place of residence:**

```{r}
t14<-lss_total%>%
  group_by(satisfied_transport)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t14%>%
  drop_na(satisfied_transport)%>%
  ggplot(aes(x=factor(satisfied_transport),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="satisfaction with the public trasportation in the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(satisfied_transport_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the public transportation in the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_transport_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the public transportation in the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_transport_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the public transportation by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_transport_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the public transportation in the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=satisfied_transport_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the public transportation in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="satisfaction with the transportation in the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=satisfied_transport_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the public transportation in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

```{r}

```

```{r}

```

### **15. Satisfaction with green spaces, public gardens and parks in place of residence:**

```{r}
t15<-lss_total%>%
  group_by(satisfied_parks)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t15%>%
  drop_na(satisfied_parks)%>%
  ggplot(aes(x=factor(satisfied_parks),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="satisfaction with green spaces, public gardens and parks in the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(satisfied_parks_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with green spaces, public gardens and parks in the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_parks_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with green spaces, public gardens and parks in the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_parks_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the green spaces, public gardens and parks in the place of residence by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_parks_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with green spaces, public gardens and parks in the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=satisfied_parks_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with green spaces, public gardens and parks in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="satisfaction with green spaces, public gardens and parks in the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=satisfied_parks_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with green spaces, public gardens and parks in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

### **16. Satisfaction with the cleanliness of the place of residence:**

```{r}
t16<-lss_total%>%
  group_by(satisfied_clean)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t16%>%
  drop_na(satisfied_clean)%>%
  ggplot(aes(x=factor(satisfied_clean),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="satisfaction with the cleanliness in the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(satisfied_clean_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the cleanliness in the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_clean_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the cleanliness in the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_clean_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the cleanliness in the place of residence by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_clean_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the cleanliness in the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=satisfied_clean_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the cleanliness in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="satisfaction with the cleanliness in the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=satisfied_clean_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the cleanliness in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

### **17. Satisfaction with garbage collection in place of residence:**

```{r}
t17<-lss_total%>%
  group_by(satisfied_trash)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t17%>%
  drop_na(satisfied_trash)%>%
  ggplot(aes(x=factor(satisfied_trash),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="satisfaction with the garbage collection in the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(satisfied_trash_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the garbage collection in the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_trash_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the garbage collection in the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_trash_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the garbage collection in the place of residence by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_trash_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the garbage collection in the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=satisfied_trash_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the garbage collection in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="satisfaction with the garbage collection in the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=satisfied_trash_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the garbage collection in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

### **18. Satisfaction with the condition of the roads and sidewalks in place of residence:**

```{r}
t18<-lss_total%>%
  group_by(satisfied_roads)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t18%>%
  drop_na(satisfied_roads)%>%
  ggplot(aes(x=factor(satisfied_roads),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="satisfaction with the roads and sidewalks in the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(satisfied_roads_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the roads and sidewalks in the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_roads_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the roads and sidewalks in the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=satisfied_roads_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the roads and sidewalks in the place of residence by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=satisfied_roads_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% satisfied with the roads and sidewalks collection in the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=satisfied_roads_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the roads and sidewalks collection in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="satisfaction with the roads and sidewalks in the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(household_income)%>%
  ggplot(aes(x=household_income,y=satisfied_roads_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% satisfied with the roads and sidewalks in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

### **19. Feeling safe while walking alone in the hours of darkness in the place of residence:**

```{r}
t19<-lss_total%>%
  group_by(feel_safe)%>%
  summarize(n=n())%>%
  mutate(freq=(n/sum(n))%>%round(3))%>%
  mutate(freq.lab=str_c(100*freq,"%"))

t19%>%
  drop_na(feel_safe)%>%
  ggplot(aes(x=factor(feel_safe),y=n))+geom_col(width=0.75,alpha=0.8,fill="dodgerblue2")+
  geom_text(aes(label=freq.lab),colour="white",vjust=1.5,size=3)+
  labs(title="Feeling safe while walking alone in the hours of darkness in the place of residence",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=(feel_safe_bi)))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence",subtitle="(%+95CI)",x="",y="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=feel_safe_bi,color=sector,group=sector))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by year and sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  filter(sector %in% c("general","ultra_orthodox"))%>%
  ggplot(aes(x=factor(year),y=feel_safe_bi,color=religiosity_level_jews,group=religiosity_level_jews))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by year and level of religiosity (Jews)",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=factor(year),y=feel_safe_bi,color=sector_multiple,group=sector_multiple))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot,alpha=0.5)+
  stat_summary(geom="line",fun.data=mean_cl_boot,alpha=0.5)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by year and sub-sector",subtitle="(mean+95CI)",x="",y="",caption="")
```

```{r}
lss_total%>%
  ggplot(aes(x=age,y=feel_safe_bi,group=age))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="Feeling safe while walking alone in the hours of darkness in the place of residence, normalized (0 to 1), 2019-2021")

lss_total%>%
  ggplot(aes(x=age,y=feel_safe_bi,color= gender))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by age group",subtitle="(mean+95CI)",x="",y="",caption="Feeling safe while walking alone in the hours of darkness in the place of residence, normalized (0 to 1), 2019-2021")
```

```{r}
lss_total%>%
  drop_na(feel_safe)%>%
  ggplot(aes(x=household_income,y=feel_safe_bi,group=household_income))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()

lss_total%>%
  drop_na(feel_safe)%>%
  ggplot(aes(x=household_income,y=feel_safe_bi,color=gender))+
  stat_summary(geom="pointrange",fun.data=mean_cl_boot)+
  labs(title="% Feeling safe while walking alone in the hours of darkness in the place of residence by household income",subtitle="(mean+95CI)",x="household income",y="",caption="2019-2021")+
  coord_flip()
```

# **Summary tables**

```{r}
lss_total%>%
  select(trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary()
```

```{r}
lss_total%>%
  select(year,
         trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary(by=year)
```

```{r}
lss_total%>%
  select(sector,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary(by=sector)

```

```{r}
lss_total%>%
  select(age,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary(by=age)
```

```{r}
lss_total%>%
  select(sector_multiple,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary(by=sector_multiple)
```

```{r}
lss_total%>%
  select(religiosity_level_jews,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary(by=religiosity_level_jews)

```

```{r}
lss_total%>%
  select(household_income,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         trust_healthcare,
         trust_healthcare_bi,
         performance_health,
         performance_health_bi,
         performance_education,
         performance_education_bi,
         trust_in_police,
         trust_in_police_bi,
         performance_police,
         performance_police_bi,
         performance_municipality,
         performance_municipality_bi,
         trust_in_knesset,
         trust_in_knesset_bi,
         performance_knesset,
         performance_knesset_bi,
         trust_in_judiciary,
         trust_in_judiciary_bi,
         trust_in_army,
         trust_in_army_bi,
         trust_in_comptroller,
         trust_in_comptroller_bi)%>%
  tbl_summary(by=household_income)
```

## **Summary tables - local services:**

```{r}
lss_total%>%
  select(trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary()
```

```{r}
lss_total%>%
  select(year,
         trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary(by=year)
```

```{r}
lss_total%>%
  select(sector,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary(by=sector)
```

```{r}
lss_total%>%
  select(age,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary(by=age)
```

```{r}
lss_total%>%
  select(sector_multiple,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary(by=sector_multiple)
```

```{r}
lss_total%>%
  select(religiosity_level_jews,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary(by=religiosity_level_jews)
```

```{r}
lss_total%>%
  select(household_income,
         year,
         trust_in_gov,
         trust_in_gov_bi,
         performance_municipality,
         performance_municipality_bi,
         satisfied_area,
         satisfied_area_bi,
         satisfied_transport,
         satisfied_transport_bi,
         satisfied_parks,
         satisfied_parks_bi,
         satisfied_clean,
         satisfied_clean_bi,
         satisfied_trash,
         satisfied_trash_bi,
         satisfied_roads,
         satisfied_roads_bi,
         feel_safe,
         feel_safe_bi)%>%
  tbl_summary(by=household_income)
```

# **Correlation Matrix**

## Correlation matrix for variables collected in 2019-2021:

*Note:* The variable "trust_healthcare" only has data for the years 2019-2020.

```{r}
lss_total%>%
  select(trust_in_gov,
         trust_healthcare,
         performance_health,
         performance_education,
         performance_police,
         performance_municipality,
         performance_knesset,
         trust_in_judiciary,
         satisfied_area,
         satisfied_transport,
         satisfied_parks,
         satisfied_clean,
         satisfied_roads,
         feel_safe)%>%
  sjPlot::tab_corr(triangle="lower",corr.method="spearman",na.deletion="pairwise")
```

## Correlation matrix for variables collected only in 2021:

```{r}
lss_total%>%
  filter(year==2021)%>%
  select(trust_in_gov,
         performance_health,
         performance_education,
         performance_police,
         performance_municipality,
         performance_knesset,
         trust_in_judiciary,
         trust_in_knesset,
         trust_in_army,
         trust_in_police,
         trust_in_comptroller,
         satisfied_area,
         satisfied_transport,
         satisfied_parks,
         satisfied_clean,
         satisfied_roads,
         feel_safe)%>%
    sjPlot::tab_corr(triangle="lower",corr.method="spearman",na.deletion="pairwise")
```

## A correlation heatmap for variables collected in 2021:

```{r}
lss_total%>%
  select(trust_in_gov,
         performance_health,
         performance_education,
         trust_in_police,
         performance_police,
         trust_in_knesset,
         performance_knesset,
         trust_in_judiciary,
         trust_in_army,
         trust_in_comptroller,
         performance_municipality,
         satisfied_area,
         satisfied_transport,
         satisfied_parks,
         satisfied_clean,
         satisfied_trash,
         satisfied_roads,
         feel_safe)%>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot::ggcorrplot(lab=T,lab_size = 1.5,type="lower",tl.cex = 5)
```


